Easy as Pi, Volume II: On the Goodput and Energy of Network Coding Schemes in the Raspberry Pi

### 2016-08-12 metrics.tex
some corrections

\subsubsection{Encoding Benchmark}
Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
made for measuring the encoding processing time. The time benchmark
is divided in two parts. In the first part, called a \textit{pre-run},
we quantify the amount of \textit{transmitted} coded packets, from
encoder 1 in Fig. \ref{fig:enc_goodput_benchmark}, required for
decoding in a single encoder-decoder link with no packet erasures
for a defined configuration of coding scheme, coding parameters and
amount of feedback. In the case of \ac{TSNC}, we also record the
points where a feedback was received from the decoder. The purpose of
the pre-run is to predict how an encoder should behave with a given
seed within its random number generator. This part of the benchmark is
not regarded as a measurement.

In the second part which is the actual \textit{simulation}, a reseted
encoder 2 in Fig. \ref{fig:enc_goodput_benchmark} is given the same
seed as in the pre-run and then we measure the time from which the
process start until we reach the amount of transmitted packets in the
pre-run. Then, this measurement is stored as the encoder $T_{proc}$
for this generic configuration.

@@

\subsubsection{Average Power Expenditure}
To extract the average power for a given configuration in our setup, we
first calculate the average current in each the idle state $I_{idle,avg}$
and the processing state $I_{idle,avg}$ for all the available sample for
the given configuration. Regardless of the current type, the average value
of the sample set of a given number of samples $N_s$ is:
%
\begin{align} \label{eq:avg_current}
I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Ampere}]
\end{align}
%
With the average current from \eqref{eq:avg_current}, we compute the average
current used for processing with respect to the idle state, by substracting
$I_{idle,avg}$ from $I_{proc,avg}$. Then, the result is multiplied by the
supply voltage to obtain the average power during the considered configuration,
given as:
%
\begin{align} \label{eq:avg_power}
P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watt}]
\end{align}
%
\subsubsection{Energy per Bit Consumption}
To get this metric for a given configuration, we simply express the energy
as the product of the average power by the processing time $T_{proc}
~[\mathrm{sec/byte}]$ obtained from the goodput measurement for the same
configuration. In this way, we can relate the processing time with the
goodput, the packet and the generation size as shown:
%
\begin{align} \label{eq:energy_per_bit}
E_b = P_{avg} T_{proc,bit} = P_{avg} \times \frac{T_{proc}}{8gB} = \frac{P_{avg}}{8R_{proc}} ~[\mathrm{Joule}]
\end{align}
%

>>>>

\subsubsection{Encoding Benchmark}
%Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
%made for measuring the encoding processing time of the considered
%coding schemes given various coding parameters.
Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
made for measuring the encoding processing time.
The time benchmark
is divided in two parts as a way to exclude the decoding processing
time from the measurements. In the first part, called a \textit{pre-run},
we quantify the amount of \textit{transmitted} coded packets, from
encoder 1 in Fig. \ref{fig:enc_goodput_benchmark}, required for
decoding a generation of packets in a single encoder-decoder link
with no packet erasures
for a defined configuration of coding scheme, coding parameters and
amount of feedback. In the case of \ac{TSNC}, we also record the
feedback packets received from the decoder. The purpose of
the pre-run is to observe how an encoder behaves with a given
seed within its random number generator.
This part of the benchmark is not measured.
%This part of the benchmark is not regarded as a measurement.
%Fig. \ref{fig:enc_goodput_benchmark} refers to the benchmark setup
%made for measuring the encoding processing time. The time benchmark
%is divided in two parts. In the first part, called a \textit{pre-run},
%we quantify the amount of \textit{transmitted} coded packets, from
%encoder 1 in Fig. \ref{fig:enc_goodput_benchmark}, required for
%decoding in a single encoder-decoder link with no packet erasures
%for a defined configuration of coding scheme, coding parameters and
%amount of feedback. In the case of \ac{TSNC}, we also record the
%points where a feedback was received from the decoder. The purpose of
%the pre-run is to predict how an encoder should behave with a given
%seed within its random number generator. This part of the benchmark is
%not regarded as a measurement.

The second part is the actual \textit{simulation}. The objective of this
part is to replicate the pre-run to obtain the encoding speed without
spending time decoding the packets.
A reseted encoder 2 in Fig. \ref{fig:enc_goodput_benchmark} is given the
same seed as in the pre-run and then we measure the time from which the 
process start until we reach the amount of transmitted packets in the
pre-run. The measurement is stored as the encoder $T_{proc}$ for
this generic configuration. For \ac{TSNC} simulations, the recorded
feedback packets are injected according to the observations in the pre-run.

%In the second part which is the actual \textit{simulation}, a reseted
%encoder 2 in Fig. \ref{fig:enc_goodput_benchmark} is given the same
%seed as in the pre-run and then we measure the time from which the
%process start until we reach the amount of transmitted packets in the
%pre-run. Then, this measurement is stored as the encoder $T_{proc}$
%for this generic configuration.

@@

\subsubsection{Average Power Expenditure}
To extract the average power for a given configuration in our setup, we
first calculate the average current in each the idle state $I_{idle,avg}$
and the processing state $I_{proc,avg}$ for all the available sample for
the given configuration. Regardless of the current type, the average value
of the sample set of a given number of samples $N_s$ is:
%
\begin{align} \label{eq:avg_current}
I_{avg} = \frac{1}{N_s}\sum_{k=1}^{N_s} I_{k}  ~[\mathrm{Ampere}]
\end{align}
%
With the average current from \eqref{eq:avg_current}, we compute the average
current used for processing with respect to the idle state, by substracting
$I_{idle,avg}$ from $I_{proc,avg}$. Then, the result is multiplied by the
supply voltage to obtain the average power during the considered configuration,
given as:
%
\begin{align} \label{eq:avg_power}
P_{avg} = V_{supply}(I_{proc,avg} - I_{idle,avg}) ~[\mathrm{Watt}]
\end{align}
%
\subsubsection{Energy per Bit Consumption}
To get this metric for a given configuration, we simply express the energy
as the product of the average power by the processing time $T_{proc}
~[\mathrm{sec/byte}]$ obtained from the goodput measurement for the same
configuration. In this way, we can relate the processing time with the
goodput, the packet and the generation size as shown:
%
\begin{align} \label{eq:energy_per_bit}
E_b = P_{avg} T_{proc,bit} = P_{avg} \times \frac{T_{proc}}{8gB} = \frac{P_{avg}}{8R_{proc}} ~[\mathrm{Joule}]
\end{align}
%

### 2016-08-12 schemes.tex
some corrections

The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
more often than $\mathbb{N} = 1$ in the original distribution, but for
the considered density range in this method, this is not a significant
modification~\cite{practicalview_tsnc2015}. Then, once the
distribution for the number of packets to mix has been defined, we
sample a value $n$ from $\mathbb{N}$ and compute $k =
\max(1,n)$. Later, we create a create a set $\mathcal{K}$ with
cardinality $k$, e.g. $|\mathcal{K}| = k$, where the elements in
$\mathcal{K}$ are the indexes of the packets that are going to be
considered for making a coded packet. To compute the indexes
of the set $\mathcal{K}$, we do the following algorithm in pseudo-code: \\
\ \\
\begin{algorithm}[H]
 \label{alg:k_set}
 \KwData{$k$: Size of $\mathcal{K}$. $g$: Generation Size}
 \KwResult{$\mathcal{K}$: The set of non-repeated indexes}
 $\mathcal{K}$ = \{ \}\;
 \While{$|\mathcal{K}| \neq k$ }{
  $i$ = Sample from $\mathbb{U}(1,g)$\;
  \If{$i \notin \mathcal{K}$}{
   Insert $i$ in $\mathcal{K}$\;
   }
 }
 \caption{Computation of the set of indexes for packet combination in SRLNC.}
\end{algorithm}
\ \\
In Algorithm~\ref{alg:k_set}, the notation $\mathbb{U}(1,g)$ stands
for a uniform discrete random variable with limits $1$ and $g$. The
pseudo-code in Algorithm~\ref{alg:k_set} indicates that the set $\mathbb{K}$
is filled with non-repeated elements taken uniformly at random from
$[1,\ldots,g]$. Finally, once the set of indexes has been defined, a coded
packet using \ac{SRLNC} can be written as shown in
\eqref{eq:sparse_coded_packet2}:
%
\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{m \in \mathcal{K}} v_{im} \otimes P_{m},\ v_{im} \neq 0,\ \forall i \in [1,\ldots)
\end{align}

@@

\ac{TSNC} can be considered an extension to \ac{SRLNC}. The key idea is
not only for the encoder to generate sparse coded packets, but also to
modify the code density of the packets progressively as required. As a
decoder accomulates more coded packets, the probability that the next
received coded packet will be \ac{l.d.} increases.

@@

The transmissions made between feedback packets are called the density
regions since the same estimated density is used for encoding sparse
packets. Once a new feedback is received, an encoder recalculates the
coding density for the new region until the next feedback packet is
received. before the coding density can be estimated, it is essential
that the encoder has a good estimate of the decoder \ac{dof}, but also
the remainder of the total budget. To calculate the density, we use
bisection to estimate a fixed density for the density region that
satisfies the budget for the $k$-th density region:
\begin{equation}
b(r(k),r(k+1),g,d) = \sum^{r(k+1)}_{i=r(k)} \frac{1}{P(i,g,d)} = \sum^{r(k+1)}_{i=r(k)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k},\ k\in [1,\ldots)
\end{equation}
%
% Where the budget is half of the remaining budget for all the density regions
% except the last one, to which it is assigned the remaining of the budget.
The feedback scheme based on the rank reports
in~\eqref{eq:feedback_dofs} roughly splits the remaining coding
regions in two halves. In other words, the first half is the region
where the encoder currently operates. Once an encoder finishes with
this region, it proceeds with second half where again it splits this
into two new regions and so on, until it finishes the transmission the
whole generation. This is also the case for the budget that is split
equally among the two new regions. The very last region will be
assigned the full remainder of the total budget and the coding density
will not vary.

>>>>

The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
more often than $\mathbb{N} = 1$ in the original distribution, but for
the considered density range in this method, this is not a significant
modification~\cite{practicalview_tsnc2015}. Then, once the
distribution for the number of packets to mix has been defined, we
sample a value $n$ from $\mathbb{N}$ and compute $k =
\max(1,n)$. Later, we create a set $\mathcal{K}$ with
cardinality $k$, e.g. $|\mathcal{K}| = k$, where the elements in
$\mathcal{K}$ are the indexes of the packets that are going to be
considered for making a coded packet. To compute the indexes
of the set $\mathcal{K}$, we do the following algorithm in pseudo-code: \\
\ \\
\begin{algorithm}[H]
 \label{alg:k_set}
 \KwData{$k$: Size of $\mathcal{K}$. $g$: Generation Size}
 \KwResult{$\mathcal{K}$: The set of non-repeated indexes}
 $\mathcal{K}$ = \{ \}\;
 \While{$|\mathcal{K}| \neq k$ }{
  $i$ = Sample from $\mathbb{U}(1,g)$\;
  \If{$i \notin \mathcal{K}$}{
   Insert $i$ in $\mathcal{K}$\;
   }
 }
 \caption{Computation of the set of indexes for packet combination in SRLNC.}
\end{algorithm}
\ \\
In Algorithm~\ref{alg:k_set}, the notation $\mathbb{U}(1,g)$ stands
for a uniform discrete random variable with limits $1$ and $g$. The
pseudo-code in Algorithm~\ref{alg:k_set} indicates that the set $\mathbb{K}$
is filled with non-repeated elements taken uniformly at random from
$[1,\ldots,g]$. Finally, once the set of indexes has been defined, a coded
packet using \ac{SRLNC} can be written as shown in
\eqref{eq:sparse_coded_packet2}:
%
\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{m \in \mathcal{K}} v_{im} \otimes P_{m},\ v_{im} \neq 0,\ \forall i \in [1,\ldots)
\end{align}

@@

\ac{TSNC} can be considered an extension to \ac{SRLNC}. The key idea is
not only for the encoder to generate sparse coded packets, but also to
modify the code density of the packets progressively as required. As a
decoder accomulates more coded packets, the probability that the next
received coded packet will be \ac{l.d.} increases~\cite{feizi2014tunable}.
\textcolor{red}{We can cite Feizi2012 here. That is the paper with the markov chain}

@@

The transmissions made between feedback packets are called the density
regions since the same estimated density is used for encoding sparse
packets. Once a new feedback is received, an encoder recalculates the
coding density for the new region until the next feedback packet is
received. Before the coding density can be estimated, it is essential
that the encoder has a good estimate of the decoder's \ac{dof}, but also
the remainder of the total budget. To calculate the density, we use
bisection to estimate a fixed density for the density region that
satisfies the budget for the $k$-th density region:
\begin{equation}
b(r(k),r(k+1),g,d) = \sum^{r(k+1)}_{i=r(k)} \frac{1}{P(i,g,d)} = \sum^{r(k+1)}_{i=r(k)} \frac{1}{1-(1-d)^{g-i}} = \frac{b}{2^k},\ k\in [1,\ldots)
\end{equation}
%
% Where the budget is half of the remaining budget for all the density regions
% except the last one, to which it is assigned the remaining of the budget.
The feedback scheme based on the rank reports
in~\eqref{eq:feedback_dofs} roughly splits the remaining coding
regions in two halves. In other words, the first half is the region
where the encoder currently operates. Once an encoder finishes with
this region, it proceeds with second half where again it splits this
into two new regions and so on, until it finishes the transmission the
whole generation. This is also the case for the budget that is split
equally among the two new regions. The very last region will be
assigned the full remainder of the total budget and the coding density
will not vary.
